VIPRE: Virtualized Intermittently-Powered Runtime Environment

### 2017-07-06 paper/paper.tex

\documentclass[sigconf,anonymous,review]{acmart}
\usepackage[normalem]{ulem}

\usepackage{amssymb} % needed for: various symbols
\usepackage{amsmath} % needed for: math symbols
% http://tex.stackexchange.com/questions/229355/algorithm-algorithmic-algorithmicx-algorithm2e-algpseudocode-confused
\usepackage{algorithm} % this used as an environment for the algorithm code (linke figure and table)
\usepackage{algorithmicx} % this is used to write the pseudo code
\usepackage[noend]{algpseudocode} % this is for the layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
% \usepackage[inline]{enumitem}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{natbib}

\usepackage{graphicx}  
\usepackage{subfigure}
\newcommand{\TODO}[1]{{\bf \em \textcolor{red}{TODO: #1}\xspace}}
\newcommand{\sys}{NAME\xspace}

@@

\title{VIPOS: Virtualized Intermittently Powered Runtime Environment (``VIPRE''?)}
% \author{
% 	\IEEEauthorblockN{Amjad Yousef Majid, Przemys{\l}aw Pawe{\l}czak}
% 	\IEEEauthorblockA{TU Delft, Mekelweg\,4, 2628\,CD Delft, NL\\
% 	\{a.y.majid, p.pawelczak\}@tudelft.nl}
% }

@@

\section{Introduction}
\label{sec:intro}
\TODO{VIPER: Virtualized Intermittent Programming model, Execution model, and Runtime environment}
\TODO{PREVIEW: Programming and Runtime Environment with Virtualized Intermittent Execution Windows}

@@

>>>>

\documentclass[sigconf,anonymous,review]{acmart}

\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{subfigure}
%\usepackage[inline]{enumitem}

\newcommand{\TODO}[1]{{\bf \em \textcolor{red}{TODO: #1}\xspace}}
\newcommand{\sys}{VIPRE\xspace}
\newcommand{\sysfull}{Virtualized Intermittently-Powered Runtime Environment\xspace}

@@

\title{VIPRE: Virtualized Intermittently-Powered Runtime Environment}

%Amjad Yousef Majid, Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m, Przemys{\l}aw Pawe{\l}czak,
%TU Delft, Mekelweg\,4, 2628\,CD Delft, NL
%\{a.y.majid, k.s.yildirim, p.pawelczak\}@tudelft.nl
%
%Kiwan Maeng, Alexei Collin, Brandon Lucia
%Carnegie Mellon University, 4720 Forbes Avenue, Pittsburgh, PA 15213, USA
%\{kmaeng, acolin, blucia\}@kmaeng@andrew.cmu.edu

@@

\section{Introduction}
\label{sec:intro}

%\TODO{VIPER: Virtualised Intermittent Programming model, Execution model, and Runtime environment}
%\TODO{PREVIEW: Programming and Runtime Environment with Virtualised Intermittent Execution Windows}

@@

\section{Computation on Intermittent Devices: Background}
\label{sec:background}

Performing complex operations on battery-less energy harvesting embedded platforms is challenging from many points of view. Here we will briefly provide a background on energy harvesting for embedded systems.

\subsection{Energy Harvesting: Background}

\subsection{(Task-based) Intermittent Computing: Background}

\begin{figure}
	\centering
	%\includegraphics[width=0.25\columnwidth]{figures/}
	\caption{Background image.}
	\label{fig:}
\end{figure}

Elaborating on the ``key challenge'' paragraphs near the end of the intro. We will need a picture.

\section{\sysfull}
\label{sec:overeall_system}

\begin{figure}
	\centering
	%\includegraphics[width=0.25\columnwidth]{figures/}
	\caption{\sys top-level description.}
	\label{fig:}
\end{figure}

Describe the overall system, the programming model, and the semantics/execution model. This should include a discussion of memory virtualization and task coalescing.

\section{Memory Virtualization}
\label{sec:memory_virtulaization}

\begin{figure}
	\centering
	%\includegraphics[width=0.25\columnwidth]{figures/}
	\caption{Memory virtualization architecture.}
	\label{fig:}
\end{figure}

\section{Task Coalescing}
\label{sec:memory_virtulaization}

\begin{figure}
	\centering
	%\includegraphics[width=0.25\columnwidth]{figures/}
	\caption{Task coalescing architecture.}
	\label{fig:}
\end{figure}

\section{Discussion}
\label{sec:discussion}

\section{Methodology and Evaluation}
\label{sec:methodology_evaluation}

\section{Related Work}
\label{sec:related_work}

\section{Conclusions}
\label{sec:conclusions}

This paper presented \sys: \sysfull.

%%%%%
